2016 Brussels Bombings

### 2019-05-26 report/report.Rmd
Add European traffic over Belgium gif
New options in animate to control # of frames in animation

@@

```{r, message=FALSE, results=FALSE}
gifname <- 'diverted'
giffile <- file.path('..', 'data', paste0(gifname, '.gif'))
if (!file.exists(giffile)) {
	ddr.animate(data$real$routes[id %in% div[, id]], giffile)
}
```
![Diverted Flights Map Animation](`r giffile`) \

@@

- Find from total flights the airlines that were most affected (from those that travel to EBBR)
- Average delays (while EBBR closed) by airline

@@

```{r, fig.align='center'}
dygraph(fuckedplot,
		main = 'Most Affected Airlines',
		ylab = 'Number of Flights',
		width = '100%') %>%
	dyRangeSelector() %>%
	dyLegend(width = '400') %>%
	dyEvent(event[1], 'Airport closes', labelLoc = 'bottom') %>%
	dyEvent(event[2], 'Airport reopens', labelLoc = 'bottom')
```

>>>>

```{r, message=FALSE, results=FALSE}
euname <- 'belgium'
eufile <- file.path('..', 'data', paste0(euname, '.gif'))
if (!file.exists(eufile)) {
	ddr.animate(data$real$routes[id %in% data$real$flights[as.Date(takeoff) == event[1], id]], eufile, nf = 1000, autocenter = FALSE)
}
```
![European Traffic Map Animation](`r eufile`) \

@@

```{r, message=FALSE, results=FALSE}
divname <- 'diverted'
divfile <- file.path('..', 'data', paste0(divname, '.gif'))
if (!file.exists(divfile)) {
	ddr.animate(data$real$routes[id %in% div[, id]], divfile)
}
```
![Diverted Flights Map Animation](`r divfile`) \

@@

@@

```{r, fig.align='center'}
dygraph(fuckedplot,
		main = 'Most Affected Airlines',
		ylab = 'Number of Flights',
		width = '100%') %>%
	dyRangeSelector() %>%
	dyLegend(width = '360') %>%
	dyEvent(event[1], 'Airport closes', labelLoc = 'bottom') %>%
	dyEvent(event[2], 'Airport reopens', labelLoc = 'bottom')
```
